---
title: "Homework 3"
author: "Sofia Perez"
date: "2026-03-04"
format: html
editor: visual
---

## Setup

```{r}
#| label: set-up
#| message: false
library(tidyverse) # general use
library(here) # file organization
library(janitor) # cleaning data frames
library(readxl) # reading excel files
salinity <- read_csv(here("data",
                         "salinity-pickleweed.csv")) # save salinity-pickleweed data as salinity
personal_data <- read_csv(here("data",
                               "Personal Data 3.4.2026.csv")) |> 
  clean_names() # save personal data as object and clean column names
```

GitHub Repository: https://github.com/sofiaperez422/ENVS-193DS_homework-03

# Problem 1. Slough soil salinity

## a.

The appropriate tests to determine the strength of the relationship between salinity and California pickleweed biomass are Pearson's correlation and Spearman rank correlation. Both of these correlation tests describe the strength of the relationship between two variables while indicating directionality, but Pearson's correlation is the parametric version that is used when there is a linear relationship between variables while Spearman rank correlation is the non-parametric version used when there is a monotonic relationship between variables.

## b.

```{r}
#| label: salinity visualization
ggplot(data = salinity,
       (aes(x = pickleweed,
            y = salinity_mS_cm,
            color = "coral3"))) +
  geom_point() +
  labs(title = "Salinity increases as pickleweed biomass increases",
       x = "California pickleweed biomass (g)",
       y = "Salinity (mS/cm)") +
  theme_minimal() +
  theme(legend.position = "none") 
```

## c.

## d.

## e.

## f.

# Problem 2. Personal data

## a.

## b.

# Problem 3. Affective Visualization

## a.

## b.

## c.

## d.

## e.

# Problem 4.

## a.

## b.

## c.

## d.
